---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# topography

<!-- badges: start -->
<!-- badges: end -->

The goal of topography is to provide configurations to some big player topography sources. These are intended
for use directly via GDAL (see for example [gdalio](https://github.com/hypertidy/gdalio)) but we only really need
text processing stuff here, no actual spatial stuff. 

## Installation

You can install the  development version from [GitHub](https://github.com/) with:

``` r
remotes::install_github("hypertidy/topography")
#options(repos = c(
#    hypertidy = 'https://hypertidy.r-universe.dev',
#    CRAN = 'https://cloud.r-project.org'))
#install.packages("topography")
```

## Example

This is a basic example showing a few sources and read via GDAL into matching grids. 


```{r example}
library(gdalio)
source(system.file("raster_format/raster_format.codeR", package = "gdalio", mustWork = TRUE))
## read as matrix
# gdalio_matrix <- function(dsn, ...) {
#   v <- gdalio_data(dsn, ...)
#   g <- gdalio_get_default_grid()
#   matrix(v[[1]], g$dimension[1])[,g$dimension[2]:1, drop = FALSE]
# }
## plot the data
gdalio_plot <- function(x, col = grey.colors(256), ..., asp = 1,  useRaster = TRUE) {
  g <- gdalio_get_default_grid()
  image(list(x = seq(g$extent[1], g$extent[2], length.out = g$dimension[1] + 1),
             y = seq(g$extent[3], g$extent[4], length.out = g$dimension[2] + 1),
             z = x), col = col, ..., useRaster = useRaster, asp = asp)
}

## set default grid to use as target
gdalio_set_default_grid(list(extent = c(50, 180, -85, -20),
 dimension = as.integer(c(1024, 512)),
 projection = "OGC:CRS84"))

## package to configure some transparent online topography sources
library(topography)

gebco <- gdalio_matrix(topography_source(x = "gebco"))
gdalio_plot(gebco, main = "GEBCO", asp = 1.6)

## for SRTM we want much smaller regions WIP

ll <- cbind(55.7558, 37.6173)[,2:1, drop = FALSE]
g <- list(extent = c(-1, 1, -1, 1) * 9000, dimension = c(512, 512), projection = sprintf("+proj=laea +lon_0=%f +lat_0=%f", ll[1], ll[2]))
gdalio_set_default_grid(g)
srtm <- gdalio_matrix(topography_source(x = "srtm_gl1"))
gdalio_plot(srtm, main = "srtm_gl1 30m", asp = 1.6)

gdalio_raster(topography_source(x = "srtm_gl1"))
```



---

## Code of Conduct
  
Please note that the topography project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
